Non-word repetition in Yélî Dnye

### 2020-09-07 manuscript.Rmd
fix character display in table
table not compiling in RStudio, though the tex file does in LaTeX separately...

knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.pos = "T")
require("papaja")
library(kableExtra)
library(gdata)
library(ggplot2)
library(lme4)

@@

pl<- read.delim("~/Documents/gitrepos/nwryd19/pl-With_yd.tsv")
palette = c( 
             "Arabic 1-2 syll" = "orange",
             "Yélî 3-4 syll"   ="navyblue",
             "Yélî 1-2 syll"  ="lightblue",
             "Italian 3-4 syll"   ="black",
             "Italian 1-2 syll"  ="gray",
             "Arabic 3-4 syll"     = "orange", 
             "Tsimane' 1-2 syll" = "green",
              "Tsimane' 3-4 syll" = "darkgreen")

myplot=ggplot(data = pl, aes(x = Age, y = Score, color = Language))+
  geom_point(aes(size = n, shape = Length))+
  geom_line(aes(linetype=Length)) + 
  theme(text = element_text(size = 16), legend.position="none", axis.text.x=element_text(colour=c("black", "black"))) +
  scale_color_manual(values = palette)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(name = "Age (years) ", breaks = c(4,8,12))+

  scale_y_continuous(name = "NWR Score", breaks = seq(0, 100, 10))+
  scale_size_continuous(range = c(2, 6))

@@

```{r tab2-stims, eval=F}
#add orthographic representations targets & other stims chars
read.delim("stimuli.txt", encoding="UTF-8")->stims
stims=stims[order(stims[,1]),-3]
colnames(stims)<-c("Type","Orthographic","Phonological")
cbindX(stims[stims$Type=="practice",],
      stims[stims$Type==1,],
      stims[stims$Type==2,],
      stims[stims$Type==3,],
      stims[stims$Type==4,])

@@

#this is leading to an error
#mytab2 = kable(stims, "latex", booktabs = T,caption="NWR stimuli in orthographic and phonological representations.", row.names =F) %>%
#kable_styling() %>%
#add_header_above(c("Practice" = 2, "Monosyll" = 2, "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))

#now that I added phonological representations, even this basic table chokes!
apa_table(stims,"NWR stimuli in orthographic and phonological representations.")
```

@@

This study was approved as part of a larger research effort by Marisa Casillas, with the research protocol having been approved by the IRB committee entitled The Ethics Committee of the Faculty of Social Sciences (Ethiek Commissie van de faculteit der Sociale Wetenschappen; ECSW) of Radboud University, Nijmegen, The Netherlands.  The approval for work outside of the Netherlands came as an amendment to the general research line on language development research (original request: ECSW2017-3001-474 Manko-Rowland; amendment: ECSW-2018-041). Participation was voluntary, with children being invited to come and participate. Regardless of how they performed, children were provided with a snack as compensation. Children who came up to participate but then refused were nonetheless provided with the snack.

@@

read.table("substitution_bank_try1.txt",header=T)->sub_bank
colnames(sub_bank)<-c("target","realization")
sub_bank$target=factor(sub_bank$target,levels=allVC)
sub_bank$realization=factor(sub_bank$realization,levels=allVC)

@@

read.table("deletion_bank_try1.txt",header=T)->del_bank
colnames(del_bank)<-c("target")
del_bank$target=factor(del_bank$target,levels=allVC)
del_tab= table(del_bank)[allVC]

read.table("match_bank_try1.txt",header=T)->match_bank
colnames(match_bank)<-c("target")
match_bank$target=factor(match_bank$target,levels=allVC)
match_tab= table(match_bank)[allVC]

#remove English meanings
trnsc$meaning[grep("English",trnsc$meaning)]<-NA

#Create proportion table
#a reasonable way to calculate proportion is the proportion of times 
#a target was produced as X out of the total number of times a target appeared
#so the denominator is not the number of substitutions (which appears in sub_tab)
#but rather the sum of sub, del, mat
#a check: colnames(sub_tab) == names(del_tab)
#a check: names(match_tab) == names(del_tab)

denom_vec=rowSums(sub_tab) + del_tab + match_tab
#THIS IS STILL BROKEN
#prop_cat=data.frame(apply(all_far,2,dodiv)*100) #generates precision because columns
#prop_cat=all_far/rowSums(all_far)*100 #generates recall because rows
#sub_tab_prop=t(t(matrix(sub_tab,ncol=length(denom_vec)))/matrix(denom_vec) )
```

@@

**TO DISCUSS TOGETHER this is higher than any previous report! can we be sure of it?**

@@

We are grateful to informants and individuals who participated in the study. AC acknowledges financial and institutional support from Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004 ACLEW, ANR-14-CE30-0003 MechELex, ANR-17-EURE-0017) and the J. S. McDonnell Foundation Understanding Human Cognition Scholar Award. MC blabla NWO Veni Innovational Scheme Grant (XXX-XX-XXX).

>>>>

knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.pos = "T")
require("papaja")
library(kableExtra)
library(gdata)
library(tidyverse)
library(lme4)

@@

pl<- read.delim("pl-With_yd.tsv")
palette = c( 
             "Arabic 1-2 syll" = "orange",
             "Yélî 3-4 syll"   ="navyblue",
             "Yélî 1-2 syll"  ="lightblue",
             "Italian 3-4 syll"   ="black",
             "Italian 1-2 syll"  ="gray",
             "Arabic 3-4 syll"     = "orange", 
             "Tsimane' 1-2 syll" = "green",
              "Tsimane' 3-4 syll" = "darkgreen")

myplot=ggplot(data = pl, aes(x = Age, y = Score, color = Language))+
  geom_point(aes(size = n, shape = Length))+
  geom_line(aes(linetype=Length)) + 
  theme(text = element_text(size = 16), legend.position="none", axis.text.x=element_text(colour=c("black", "black"))) +
  scale_color_manual(values = palette)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(name = "Age (years) ", limits = c(4,12), breaks = c(4,8,12))+

  scale_y_continuous(name = "NWR Score", limits = c(0,100), breaks = seq(0, 100, 10))+
  scale_size_continuous(range = c(2, 6))

@@

```{r tab2-stims}
#add orthographic representations targets & other stims chars
stims <- read_delim("stimuli2.txt", delim = "\t")
stims=stims[order(stims[,1]),-3]
colnames(stims)<-c("Type","Orthographic","Phonological")
cbindX(stims[stims$Type=="practice",],
      stims[stims$Type==1,],
      stims[stims$Type==2,],
      stims[stims$Type==3,],
      stims[stims$Type==4,])

@@

# mytab2 = kable(stims, "latex", booktabs = T,caption="NWR stimuli in orthographic and phonological representations.", row.names =F) %>%
# kable_styling() %>%
# add_header_above(c("Practice" = 2, "Monosyll" = 2, "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))
# mytab2

#now that I added phonological representations, even this basic table chokes!
# apa_table(stims,"NWR stimuli in orthographic and phonological representations.")
```

@@

This study was approved as part of a larger research effort by **@ac add info from Middy's FAIR reply**. Participation was voluntary, with children being invited to come and participate. Regardless of how they performed, children were provided with a snack as compensation. Children who came up to participate but then refused were nonetheless provided with the snack.

@@

read.table("substitution_bank.txt",header=T)->sub_bank
colnames(sub_bank)<-c("target","realization")
sub_bank$target=factor(sub_bank$target,levels=allVC)
sub_bank$realization=factor(sub_bank$realization,levels=allVC)

@@

read.table("deletion_bank.txt",header=T)->del_bank
colnames(del_bank)<-c("target")
del_bank$target=factor(del_bank$target,levels=allVC)
del_tab= table(del_bank)[allVC]

#remove English meanings
trnsc$meaning[grep("English",trnsc$meaning)]<-NA
```

@@

** this is higher than any previous report! can we be sure of it?**

@@

We are grateful to the individuals who participated in the study. The collection and annotation of these recordings was made possible by Ndapw:éé Yidika, Taakêmê Ńamono, and Y:aaw:aa Pikuwa; with thanks also to the PNG National Research Institute, and the Administration of Milne Bay Province AC acknowledges financial and institutional support from Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004 ACLEW, ANR-14-CE30-0003 MechELex, ANR-17-EURE-0017) and the J. S. McDonnell Foundation Understanding Human Cognition Scholar Award. MC acknowledges financial support from an NWO Veni Innovational Scheme grant (275-89-033).
